---
title: "Time Series - AR, MA, ARMA & ARIMA"
output: html_notebook
---
```{r}
install.packages("devtools")
```
```{r}
install.packages("forecast")
```


```{r}
#load packages
library(IRdisplay)
library(magrittr)
library(tidyverse)
library(scales)
library(gridExtra)
library(forecast)
library(tseries)
library(ggthemes)
```

Load the file

```{r}
nflx <- read_csv("NFLX.csv")
head(nflx)
```


```{r}
#check class

class(nflx$Date)
```
```{r}
summary(nflx$Adj_Close)
```


## Check for Stationary
```{r}
#check time series plot
ggplot(nflx, aes(Date, Adj_Close)) + geom_line(colour='blue') + ggtitle("Netflix Closing Stock Prices")+ geom_smooth(method = "lm", formula = y ~ x, colour='black', linetype = "dashed")

```



```{r}
# check ACF plot
ggAcf(nflx$Adj_Close, type='correlation')
```



```{r}
#run ADF test
adf.test(nflx$Adj_Close)
```


## Transforming for Stationary  and Identifying Model Parameters 
```{r}
#fit AR model
ar.model <- auto.arima(nflx$Adj_Close, max.d = 0, max.q = 0, allowdrift = T)
ar.model
```


```{r}
# fit MA model
ma.model <- auto.arima(nflx$Adj_Close, max.d = 0, max.p = 0, allowdrift = T)
ma.model
```


```{r}
#fit ARMA model
arma.model2 <- auto.arima(nflx$Adj_Close, max.d = 0, allowdrift = T)
arma.model2
```


```{r}
#fit ARMA model
arma.model <- auto.arima(nflx$Adj_Close, max.d = 0, allowdrift = T)
arma.model
```


```{r}
# fit ARIMA model
arima.model <- auto.arima(nflx$Adj_Close, allowdrift = T)
arima.model
```

## Checking the Residuals of the Model Fit

```{r}
# calculate residuals of each model
ar.residual <- resid(ar.model)
ma.residual <- resid(ma.model)
arma.residual <- resid(arma.model)
arima.residual <- resid(arima.model)
```


```{r}
# plot PACF of each models residuals
ggAcf(ar.residual, type = 'partial')
ggAcf(ma.residual, type = 'partial')
ggAcf(arma.residual, type = 'partial')
ggAcf(arima.residual, type = 'partial')
```


```{r}
#run the Ljung Box test on the residuals
Box.test(ar.residual, type='Ljung-Box', lag=1)
Box.test(ma.residual, type='Ljung-Box', lag=1)
Box.test(arma.residual, type='Ljung-Box', lag=1)
Box.test(arima.residual, type='Ljung-Box', lag=1)
```

## Making a Forecast of each Model

```{r}
# make forecast for each model
ar.forecast <- forecast(ar.model, h=60, level= 90)
ma.forecast <- forecast(ma.model, h=60, level= 90)
arma.forecast <- forecast(arma.model, h=60, level= 90)
arima.forecast <- forecast(arima.model, h=60, level= c(80, 95))
```

```{r}
# plot forecast for each model
g1 <- autoplot(ar.forecast)
g2 <- autoplot(ma.forecast)
g3 <- autoplot(arma.forecast)
g4 <- autoplot(arima.forecast)
grid.arrange(g1, g2, g3, g4, nrow=2, ncol=2)
```
```{r}
g5 <- autoplot(arima.forecast) 
g5
```

## Fitting Seasonal Trend Loess (STL) Decomposition Models
```{r}
# transform to time series object; need to specify frequency
prices.ts <- ts(nflx$Adj_Close, frequency = 12)
```

```{r}
# fit stl model
stl.model <- stl(prices.ts, s.window = 'periodic')
```


```{r}
# plot model fit
autoplot(stl.model)
```


```{r}
# make forecast
stl.forecast <- forecast(stl.model, h=60, level=90)
autoplot(stl.forecast)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
